data_collation

### 2024-04-12 scripts/data_collation.Rmd
updated fish, mmorph, and kelp data

# Load libraries 
```{r}
library(plyr)
library(dplyr)
library(tidyverse)
```

@@

@@

# remove columns with observer and unneeded data
morph_data <- morph_data[ -c(11:14) ]
```

@@

@@

# remove columns with observer and unneeded data
fish_data <- fish_data[ -c(10:13) ]

# look at fish_Aggregated later, this is kelp density possibly?

>>>>

# Load libraries 
```{r}
library(plyr)
library(dplyr)
library(tidyverse)
library(lubridate)
```

@@

# Use lubridate to format date to be consistent
kelp_data$DATE <- mdy(kelp_data$DATE)

# Rename King's Beach to Kings Beach
kelp_data$SITE[kelp_data$SITE == "King's Beach"] <- "Kings Beach"

# output updated dataframe
write.csv(kelp_data, "output/cleaned_data/kelp.data.clean.csv", row.names = FALSE)
```

@@

# remove columns with observer and unneeded data
morph_data <- morph_data[ -c(11:14) ]

# Make all columns capitalized
colnames(morph_data) <- toupper(colnames(morph_data))

# Use lubridate to format date to be consistent
morph_data$DATE <- mdy(morph_data$DATE)

# output updated dataframe
write.csv(morph_data, "output/cleaned_data/morph.data.clean.csv", row.names = FALSE)
```

@@

# Fish data is cleaned and ready

@@

# remove columns with observer and unneeded data
fish_data <- fish_data[ -c(10:14) ]

# Use the actual size data to bin into the size classes to combine with other dataframe
fish$SIZE <- cut(fish$actual_size, breaks = c(0, 10, 20, 30, 40, 50, 70, 100, Inf),
               labels = c("< 10", "10_20", "20_30", "30_40", "40_50", "50_70", "70_100", "> 100"),include.lowest = TRUE, right = FALSE)

# combine updated dataframes
fish_data <- left_join(fish, fish_data)

# remove columns with VIS
fish_data <- fish_data[ -c(14) ]

# Use lubridate to format date to be consistent
fish_data$DATE <- mdy(fish_data$DATE)

# output updated dataframe
write.csv(fish_data, "output/cleaned_data/fish.data.clean.csv", row.names = FALSE)

# look at fish_Aggregated later - Austin, this is kelp density possibly?
